Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-05-08 appendix.tex
final to IRC with appendix ?

% !TEX root = paper.tex
\appendix
\section{Model comparisons of the Individual flow harmonics $v_n$}
\label{sec:vn}
As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics. Therefore it is important to check how well the individual flow harmonics $v_n$ are produced in the theoretical models used in Sec~\ref{sec:theory}.

@@

The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_8}, where the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
The calculations captures the centrality dependence of $v_n$ in the central and midcentral collisions with a precision better than 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.

@@

The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to $v_n$ data in Fig.~\ref{fig:Figure_9}.
Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$. More specifically, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 could nicely fit $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges. For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions. Compared with these two calculations, hydrodynamic calculations with AMPT initial conditions improves the descriptions of $v_n$ (n = 2, 3, 4). Overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_2$ and $v_3$,  50\% for $v_4$. The calculations with AMPT initial conditions describe the data better with the precision 10-20\%

@@

The individual flow harmonics $v_n$ (n=2, 3 and 4) are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_10}.
The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ as shown in Fig.~\ref{fig:Figure_10} with a precision about 10-20\% for $v_2$ and 10\% for $v_3$ and $v_4$. The version based on the string melting configuration without the hadronic rescattering phase underestimates the data quite a bit, which demonstrates that a large fraction of the flow is developed during the late hadronic rescattering stage in the string melting version of AMPT.
However the default version of AMPT underestimates $v_n$ by $\approx$ 20\%. It should be noted that the default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_modelcomparisonBest.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_modelcomparisonBest.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_modelcomparisonBest.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the best models for each theory model.}
        \label{fig:Figure_11}
              \end{center}
\end{figure*}

Finally, only the best calculations from three models are compared to the $v_n$ data in Fig.~\ref{fig:Figure_11}.
The calculations from the event-by-event EKRT+viscous hydrodynamic, VISH2+1 with AMPT initial conditions ($\eta/s$ =0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ (n=2, 3 and 4) with a precision of 5-20\% in general and the centrality dependence differs in three models as well as in different order harmonic flows.
The simultaneous description of all order individual flow harmonics $v_n$ is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions together with SC$(m,n)$ and NSC$(m,n)$.

>>>>

% !TEX root = paper.tex
\appendix
\section{Model comparisons of the Individual flow harmonics $v_n$}
\label{sec:vn}
As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$. Therefore it is important to check how well the theoretical models used in Sec~\ref{sec:theory} describe the measured $v_n$ data~\cite{Adam:2016izf}.

@@

The measured $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_8}. In these calculations the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
The calculations captures the centrality dependence of $v_n$ in the central and midcentral collisions with a precision better than 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.

@@

The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the $v_n$ data in Fig.~\ref{fig:Figure_9}.
Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$. More specifically, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 could nicely fit $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges. For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions. Compared with these two calculations, the calculations with AMPT initial conditions improves the descriptions of $v_n$ (n = 2, 3 and 4). Overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ (n = 2 and 3),  50\% for $v_4$. The calculations with AMPT initial conditions describe the data better with the precision 10-20\%.

@@

The AMPT calculations with various configurations are compared to the $v_n$ data in Fig.~\ref{fig:Figure_10}.
The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ as shown in Fig.~\ref{fig:Figure_10} with a precision about 10-20\% for $v_2$ and 10\% for $v_3$ and $v_4$. The version based on the string melting configuration without the hadronic rescattering phase underestimates the data quite a bit compared to the calculations with the string melting version of AMPT, which demonstrates that a large fraction of the flow is developed during the late hadronic rescattering stage in the string melting version of AMPT.
The default version of AMPT underestimates $v_n$ (n = 2, 3 and 4) by $\approx$ 20\%. It should be noted that the default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_modelcomparisonBest.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_modelcomparisonBest.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_modelcomparisonBest.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to few selected model calculations from three theoretical models which describe the $v_n$ data best.}
        \label{fig:Figure_11}
              \end{center}
\end{figure*}

Finally, few selected calculations from three theoretical models which describe the $v_n$ data best are shown in Fig.~\ref{fig:Figure_11}.
The calculations from the event-by-event EKRT+viscous hydrodynamic, VISH2+1 with AMPT initial conditions ($\eta/s$ =0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ (n=2, 3 and 4) with a precision of 5-20\% and the centrality dependence differs in three models as well as in different order flow harmonics.
The simultaneous description of all order individual flow harmonics $v_n$ is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions together with SC$(m,n)$ and NSC$(m,n)$.

### 2017-05-08 longSC.tex
final to IRC with appendix ?

%The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
Anisotropic flow~\cite{Ollitrault:1992bk} is quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:

@@

An important input to the hydrodynamic model simulations is the initial distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricities $\epsilon_n$~\cite{Alver:2010gr},
\begin{equation}
 \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
  \label{eq:eccentricities}
\end{equation}
where the curly brackets denote the average over the transverse plane, i.e. $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g. $v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
Harmonic $v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
Therefore, the higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}. When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitudes of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ are sensitive to the ansatz used for the viscous distribution function, and to the correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
Hence, studies of the correlations between higher order ($n>3$) and lower order ($v_2$ or $v_3$) harmonics and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.

@@

The SC observables are defined as:
 %
%\begin{widetext}
\begin{eqnarray}
\left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
&&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
&=&\left<v_{m}^2v_{n}^2\right>-\left<v_{m}^2\right>\left<v_{n}^2\right>\,,%\nonumber\\
%&=&0\,.
\label{eq:4p_cumulant}
\end{eqnarray}
%\end{widetext}
%
with the condition $m\neq n$ for two positive integers $m$ and $n$ (for details see Sec.~IV~C in~\cite{Bilandzic:2013kga}).
In this article SC($m$,$n$) normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq} is denoted by NSC($m$,$n$):
%
\begin{equation}
\mathrm{NSC}(m,n) \equiv \frac{\mathrm{SC}(m,n)}{\left<v_{m}^2\right>\left<v_{n}^2\right>}\,.
\label{eq:nsc}
\end{equation}
%
Normalized symmetric cumulants reflect only the strength of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics. In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta|>1.0$ which suppresses biases from few-particle nonflow correlations. For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}) the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this observable. This was verified by HIJING model simulations in \cite{ALICE:2016kpq}.

@@

The centrality dependence of the SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short lifetime. To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
The AMPT model can be run in two main configurations, the default and the string melting model~\footnote{The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.}.
In the default version, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}. In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}. These partons are then combined into the final state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
The third version used in this article is based on the string melting configuration in which the hadronic rescattering phase is switched off to study its influence on the development of anisotropic flow. 
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV (see Appendix~\ref{sec:vn} for the quantitative comparisons). It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for the quantitative disagreement~\cite{Adam:2016nfo}. The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.

>>>>

%The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
Anisotropic flow~\cite{Ollitrault:1992bk} is quantified with $n^{\mathrm{th}}$-order flow harmonics $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:

@@

An important input to the hydrodynamic model simulations is the initial distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricities $\epsilon_n$~\cite{Alver:2010gr},
\begin{equation}
 \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
  \label{eq:eccentricities}
\end{equation}
where the curly brackets denote the average over the transverse plane, i.e. $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonics, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g. $v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
Harmonic $v_4$ and higher order flow harmonics can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
Therefore, the higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}. When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitudes of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ are sensitive to the ansatz used for the viscous distribution function, and to the correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
Hence, studies of the correlations between higher order ($n>3$) and lower order ($v_2$ or $v_3$) harmonics and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.

@@

The SC observables are defined as:
 %
%\begin{widetext}
\begin{eqnarray}
\left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
&&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
&=&\left<v_{m}^2v_{n}^2\right>-\left<v_{m}^2\right>\left<v_{n}^2\right>\,,%\nonumber\\
%&=&0\,.
\label{eq:4p_cumulant}
\end{eqnarray}
%\end{widetext}
%
with the condition $m\neq n$ for two positive integers $m$ and $n$ (for details see Sec.~IV~C in~\cite{Bilandzic:2013kga}).
In this article SC($m$,$n$) normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq} is denoted by NSC($m$,$n$):
%
\begin{equation}
\mathrm{NSC}(m,n) \equiv \frac{\mathrm{SC}(m,n)}{\left<v_{m}^2\right>\left<v_{n}^2\right>}\,.
\label{eq:nsc}
\end{equation}
%
Normalized symmetric cumulants reflect only the strength of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$. In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$ which suppresses biases from few-particle nonflow correlations. For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}) the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this observable. This was verified by HIJING model simulations in \cite{ALICE:2016kpq}.

@@

The centrality dependence of the SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short lifetime. To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
The AMPT model can be run in two main configurations, the default and the string melting model~\footnote{The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.}.
In the default version, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}. In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}. These partons are then combined into the final state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
The third version used in this article is based on the string melting configuration in which the hadronic rescattering phase is switched off to study its influence on the development of anisotropic flow. 
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV (see Appendix~\ref{sec:vn} for the quantitative comparisons). It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for the quantitative disagreement~\cite{Adam:2016nfo}. The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
